Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-07-26 doc/ms.tex
Remove sentence describing asserting Ni mixing is only explanation for SN
Include text with a comparison between 16abc and 11fe for the B-V colors.

\section{First Light And Explosion Time}
\label{sec:first_light}

@@

@@

We conclude that the early observations of \abc\ can be explained if the $^{56}$Ni synthesized in the explosion is mixed into the outermost layers of the SN ejecta.

>>>>

\section{Early Observations}
\label{sec:first_light}

Here we consider our suite of early observations of \abc, and compare our findings with SN\,2011fe, a well-studied, nearby SN that was discovered shortly after explosion \citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.

@@

\subsection{Blue Optical Colors Shortly After Explosion}

Multiband observations of \abc\ began $\sim$1.5 d after discovery, which allows us to trace its color evolution starting $\sim$1.7 d after $t_0$. In Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\ and SN\,2011fe, where the observations of SN\,2011fe are taken from \citet{2016ApJ...820...67Z}. For both SN the colors have been corrected for the total inferred redenning along the line of sight. Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before eventually becoming as blue as \abc.

\begin{figure}[]
  \centering
  \includegraphics[width=0.45\textwidth]{16abc_11fe_colors.pdf}
  \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
    compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
    photometry are calibrated on the Vega system. The data for 
    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
  \label{fig:B-Vcolors}
\end{figure}

Roughly 16 d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe. Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017arXiv170608990H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs. While there are many factors that contribute to the early optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors are often interpreted as a hallmark of interaction between the SN ejecta and a binary companion. Nevertheless, it is interesting to note that despite the blue optical colors the UV $-$ optical colors of \abc, SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs than the UV $-$ optical colors of iPTF\,14atg \citep{2015Natur.521..328C}, the most likely candidate for an ejecta-companion interaction SN.

@@
